\documentclass{article}
\begin{document}

It was a dry and hot summer day, 
when the expedition began to form in the Borderlands of Bohemia.

On one side, neatly cut grass burnt brown, and on the other, the anarchic flourishing
of wildflower meadows when left to nurture,
visualized the binary logic of the trinity all too well,


but the positive outlook on embarking a České dráhy train, 
upon a journey with its defined
tracks of tight curves and steep inclines lifted my spirits.

Miss Bryant is the opposite, 
her blathering and gamboling under my tutelage, 
and parading her sad, weighty breasts

prodding to the centre of gravity of her sex

makes her a flat hypertextual, uncontrolled link up. 

a child
interlocutor



"The best we can have is pulp", I mumble to myself,
intelligence is the ability of a living creature, 
to perform pointless and unnatural acts
unlike a machine

if she wants to be at the centre, 
she must be driven to the edge - 
she is perfect for the mission.




The sun is alarmingly noisy, 



The constant deterritorializations 
have made me incapable of throwing up,
so I'm dreaming of choking
and putting my foot on the throttle 
until the engine sets everything on fire, 
toxic smoke will pollute the skies and fall down as black icicles.

We were both eager to leave the territory of conflict, 
and the, for my taste, too hot continental surface, 
and its politics of preemptive power to colonize the future land. 

A heavenly space where sky reconnaissance aircrafts 
hovering over to pinpoint the slightest nullity and react with friendly fire, 
no other option to join this silly cyberwar and digging trenches for defense, 
only to fill them by digging another one,
a gridlocked situation, 
solitary kamikaze attacks.

bunker
The absence of another writer with whom I would be able 
to experiment with current Bataillian philosophy 
and to divert me from the terrors of militarized 
useless deconstruction, excavation  of the mind.

Teached me the lesson to object surfaces, 
rather than falling for the imbeciltiy of hollowing out too deep, 
excavating infinite meaning, 
which is intrinsic in the soil, 
and leave it for evermore. 

A fellow sonic blowing a French horn to feel a vibration of the body, 
covered by a film, implanted memory, that never happened. 

senses
friction of constant psyop, of not speaking trauma. 


philosophia perennis


Confused I was wandering the deserted station, 
a junction   
when an elderly man man approached me, "May I be of assistance?", he was asking in broken German,
I was relucant at first as he looked like one of those collectors of curiousities wating in his little shop of horrors to palm a cursed thing off on some naivete.
I went asking for the train to Klatovy, He pointed on the train on the rear track 4, which should have been departed a long time ago. 

The conductor, a young and very tall, lean lad, which catched my attention as he was one of those seldom hybrids of the old and the new, a fit athlete of body and mind. Characteristics needed, whistle strong
to signal departure of the train at each stop.
A spiritual wayfarer, 

His repeatedly hyperbolical pronounciation of my destination 
Lipno nad Vlatinou, Lipno nad Vlatinou, left room for much speculation.









This research "paper", 
or rather the absence of hard-coded material,  

palimpsest, to substantiate my meth of alchemy. 

resounding of carbon on membrane due to a
malfunction of our devices and the
abundance of plumbago. 

serves as a detailed account
of the events that occured in the fall of 2022.

"Youth is the most fairest time", gran Elisabeth always sad, 
What a delusion! 
which occurs, when the lifespan of a mind is only understood in a backwards lineage,
through unreliable memory.

Puberty is the most dangerous, violent passage, 
where the inner wants to copulate with outer struggle 
energy and melancholia, intertwine
a longing for premature death, to escape the reality of 
grinning zombies.

Anyway, to recraft the mechanical body into biological,

to reach the cosmogenic process of synthesis, 
and guffawing Erin, 
wants to go voluntarily in btw! What could possibly go wrong?


I am trying to imprint meaning 
on this hideously filthy and ugly inked coating,
veiling a supposedly innocuous device, 
which is an intermediate thing between a tool and machine.


A system with deficiencies,
but the analogous application permits emergence of logic, 
which is dependent on the syntax of my native language. 

As a woke man, I am also inverting the gender of writing. 
She blares, I type. Typing is writing. 
No compromise, a strict diktat
the real, no simulation

immediate of command and control. 
That pure communication of junglenized warfare. 

Typing blind, 
I cannot see what I write, on the Nietzschean ballwriter, 
globe


The gapping wound (rictus) widens, 
stretched wide open by her own hands, 

manipulating the open wound with a stick to extract more information. 


I am banging so hard, a record of streaming to become immortal, 
a crack,and the losened hole surrendered, as if ruined by magic. 


An animate puppet, like living dead, 


vibrating diaphragm sets in motion the pen 
which in turn writes on the moving lubricant

saliva and mucus, 
distilled from her mouth and rectum to get to substance /quintessence. 
rectal temperature goes down
life spiralling towards 0, 

the better part of an hour

a peculiar 
rictus twisted the right side of her face, as if the nerve 
had been pulled on a string



the whirling membrane like a dervish
in a pulsating, pounding beat, that is connecting me with the beyond.  
Sama-zan in this ceremony, 
a rave of self-destruction
as its repetitive rythm and frequency spectrum 
will long awaited awakening of Krakonoš.

in his greatness of god, 

not killed,
sacrifice in exchange for a more bearable life
and limited consciousness.

which brings forth the apocalypse.


crushed the unknown with layers of bureaucrazy. 
A monstrosity, which nonhumans call the "normal",
and in which forms of rampant intelligence are blighted. 

Bureaucrats haven't been on that fatal  cool trip Erin went,
direct access to the correlation, 
pneuma that only art and poetry understands. 

well provided for the morrow, looking forward with glee


Inhumans, including myself, got too curious, and dared to study cursed books,
I have no intention to point at unknown knowns, 
material of endless density,
that will possess the noumena with its claws, sharp teeth. 

What followed was a phase of performing senseless data science in python, 
for weeks, or even months, I cannot recall,  
as I have totally lost the order of time.

I've developed a wicked insomnia, which I've tried to compensate with a couple of hourse of rest before the clock strikes noon. 
u/acc, \#rhett, \#cave
To read the cursed book, some men will literally instead of going to therapy.
after cyber sex it gets weird.
This booby trap, blackmailing me with cringe and sins into doing stuff,

tor down


London sent me on this research residency to investigate paranormal incidents, 
which had to do with the inexplicable missing of two astronauts, not knowing
trapped here forever.
Here I should perform under the motto of the secret intelligence service  
Semper Occultus. 

But what I found there in Forest Sauvage, which needs to be DESTROYed by acid rain, 
was beyond any comprehension.

Despite the myth of economic growth, 
both to my great delight and deep sorrow, 
I found a shining example of hyperaccelerationism.
not capital though
Everything was about control, social relation, 
life itself
The residents, including less suspicious, newly arrived immigrants,
were lured into this safety net and truly believed in it. 
Unaware of how out of control everything really was. 


of the Old Ones, past cultures, primitive speculative knowledge, 
lost

basilisks
The four horseman of the apocalypse. 
My fancy for 
Immutable, smart contracts, transactions, words
his dark voice 


An unpleasant MI5SON, easy for bellends 
bureau from the security service, who are into domestic counter-intelligence. 
the only thing to keep stiff, his upper lip.
Like Matthew Fox, known as K, co-founder and my best fiend, in this intelligence machinery. 
unavoidable experiments, went into combat
"thought-experiments" not from armchair but the battlefield.

communication between materialists and vitalists extremists problematic, 
the common ground is the brain, that has been shattered. 

idea of spiritual appearance which was casted in the fascist realm?soul
materialsts hardened


As a veteran analyst and natural philosopher, 
I was never able to translate my copious inventions into long-term
financial success. 
to mar
In truth they wanted to get rid of me, deemed uncomfortable
placed on the retired list as "unfit for service"
due to spacesickness. 
And this is not due to the spinning of the earthcore
but, 
the organised surface of reality, excavated and flat dried out in the sun.

that I inappropriately mingled with the RAF.

This military strategy forced my retreat into the Outside, 

'I' was born out of crisis, but the irony is, 
whilst I was sent to prison, and you know who you are, 
and which so well benefited us, what is left of modern 'society' live in cells now,
in isolation.
losing connection to home, as in the control center skeletons.

 
because of my stream of blood.
Partly, I share it with my indiginous ancestors, who lived on this land 
for many generations. 
witch mother, from the émigré community.
a stamp of strangeness




I am classified as genetic trash even though I posess natural
machine vision on my left eye, on this geometric field of the chess game
random rectangles in different sizes with colors from the RGB spectrum
filling the colon with air, pressure eye pops
Patient 0, 
my hearing performance is extraordinary
interpretation sounds ghosts.
The frames switch on and off
simultanously
as my mental functions, such as perception, memory and attention
vision, movement, sensation, coordination
did not match the requirements of the MI5.
even though I'm much more qualified than those hoes.

I've lost an eye, stabbed it
with fountain pen. 
Also I adopted the motto "Every man his own stylo", 
so I sent K a letter invisible ink. 



Autonomous engineered matter, intelligent materials
process environmental stimuli and adapt. 
living material
I suffer from distorted reality perception, completely neurotic. 


</p>
-----------------------------

<p>


On orders from the Inside, 
moving through the most impassable jungle area,
I was greeted by many surprises, some shockingly awful, some delightful.

An avalanche backwards to the past,
atavism=reappearance of genetic old features
Moorhead is the werewolf-rat, Erin is her past
animality is the undercurrent of modernity and reality
conditions like the triassic period
adapt for survival in the new environment
Lamarckism, strong liver from drinking, so son inherits also strong liver

Most biological memories are unpleasant, the ones echoes of danger and
terror, nothing endures so long in the flesh like FEAR, 
ADHS, red face
the mind /consciousness dreams of good times, nostalgia, a state
we call the waking life.
but what about the dreams we are not aware of /remember


A severe insomnia, for weeks or months , I can't recall, 
as I totally lost the sensation of time
not tired but animated, driven by an hithero unknown inner force, 
I was gifted a horse for my examinations, 
by the britsh /canadian forces.  
, although oncerned what will do this to my brain structure, 
might die happy
systemctl start, 
experiment with electric fire, record player, alarm clocks, paraloid mirror,
aural rohrschach test, a sonic sculpture, what images do sound create
sadness, cheer, power,
actually better than visual, vibrating the flesh, more direct
(36/37), 


Empirical approach, observing with the senses, 
the techno-logical extensions, is all we can do, global village.

The biologist Bodkin (p. 38/The drowned world), that consciousness is nothing more than a special category of cytoplasmic coma that the nervous system developed
appearance of dinos, huge lizards so humans would revert back to apes?





So I came across this poor monkey covered in dust, 
as soon we made contact with his big brown eyes, his shy little smile at the realisation that he is alive 
that would melt the stoniest of hearts and minds!
On thorough washing, which I thought it truly necessary, I accidently broke his hand, which he needed for writing. He already lost one foot due to Plantar Faciities,
a remnant from the past

,
I felt so bad for the poor thing, I've started to nurture for him and let him rest on my wide chest. On that evening I've noticed a strange weather phenomenon, the sky turned orange, knowing he sent me an immesurable amount dust particles. 


The General in China whispered on the wireless
that the ape is an Arian Nazi and must be decapitated.
And why shouldn't I have been fooled by his cute appearance?
Fleet Street tabloids picture him as a inane, clumsy Gorilla
blanking out the danger that comes with the true nature of that brute inhumane beasts,
On afterthought, what would have been the consequences, to attack him. 
A trap that was set up by the jealous General, 
who knows my sweet-tempered nature too well, instead of killing I've locked him in the basement for a couple of days. 
Until the phase of hysteria was over, and came to my senses.
We became loyal companions since ever, clothing him bespoke London couture, 
gay Clothing protection from having sex. 
wandering through the forest, sleeping beside me and sentinelling my camp, when I go on short excursions.
Love, that made me to build solid Wolfsgrub, instead of dwelling in that transitory French military tent.
In that platonic cave, drunk with love, 
my feelings toward, the most beautiful and pure creature.
 

Their horsemen ride one behind the other, not next to each other.
no soul, how could hold flesh together?
connected by technology. 
conduits, easy to take over. 
when searching in their cables, could only find me.
Le Chant du loup, helpless with and without their tech,  
that's when John came into play. 
in the cold, trap, maladapt.
adaption to change=survival. 
trolley problem.

Pneuma is not accessible to humans and has been made into a quasi-substance (solid), a representative, 
that is attached to regions of existance, like the jet of a black hole. 

The expedition together with Erin Bryant, a pundit,
because of her extensive academic background, 
or maybe because she just fucked around. 
Hapless visitors as we were, 


We had only nonlethal weapons with us,
for example a acoustic hailing and disruption (AHAD) device,
delayed auditory feedback (DAF),
to shut her up.

Neuralgia, depression, nervous breakdown, the symptoms that Eros, the life force, 
animal magnetism, has been buried with language, interweaved with the flesh.
The soul is the hole, the body the solid. 
Modernity made spirit the primary instrument, which is needed to pneuma and body are blind to each other, a relation to introduce them politely to each other, but has been the prime divider, and trying to keep them apart. 
Not able to put into words, so I've took action. 

</p>


<h6>Der Chasseur im Walde</h6>
turn around<br>
to see if there is someone behind you
attached 
never recognise to be seen

evidence of megalithic monuments
a total eclipse

where are we now?
says brilliant speaker
in the Spiegel cabinet 
of Stonenge
is it you?

wolves moan 
9 ways to get to know a stone
Material bonded somehow
kissed by transformative cosmic energy.
Wolves howling at the moon, in hope for contact, 
who is not bloated with reason and morality. 
</p>

<p>
From afar I see a green mountain.
A small serpentine footpath, true love travels on a gravel road, 
into the virgin forest. 
On our way I notice a goshawk, motionless in the sky, until it fell from the sky, 
to devour its cute prey,
I wait for some action, but it kept disappearing.



On entering nothing specific attracted our attention 
consumated by this complex whole.
The deep we've stepped into, we only noticed the enormous silence, 
as if all life was eradicated but ours. 
Like being drowned in deep outer space, in a vacuum which is filled
with alien noise, of matter, which we, nor our scientific devices  could perceive.
Are we part of this alien environment?
Against my upbringing, and conduct as a scientist, 
I was just in desperation to hear something, which made me to kick a piece of wood
which I assumed to be dead.
The potent response was a gruesome finding. 
A teeming mass of now open cells in 
a structure of magnificent civil engineering  countless
wander past antigen-presenting cells 
each? many of them carrying eggs?, always on the lookout
for the right binding parnter for their antigen receptor.  

I walk past the mighty pillars, symbols what do they signify, human made
4 - the orange graphity tells, and I feel strangely alarmed by that number. 

I'm occupied with investigating another assumingly familiar structure,
a cabin filled with boxes. 


what is behind creation: randomness or design 
the wasp don't know, who is pulling the strings.
but part of environment, no one is pulling strings.
happy that someone else is pulling strings, but alone.
what does the spider make of the web? 
catch prey, 
can it see the beauty?
The interrogation felt a bit of safety,
when a massive flying swarm of drones comes from behid
Still shocked, I decide  to re-enter the main path
just a few steps on, I discover the potential nutrition source of the workers,
a small field of hideously  ugly plants, flowering in pink.
I can't tell what repels me, they don't belong in there?
their uncontrolled growth ? or, better put, if I look closer. 
what gross things I could find there? 
I walk deeper in the forest, always further drawn into it
with the faith in me
there must be some point of reference.
</p>

<p>
The three body problem 
nuclear family. 


I see a couple heading towards me, 
the man walks in front, the woman behind.
We greet each other politely,
oddly strange in this hostile solitude, wild habitat.


The first impulse of asking them about 
location determination,
that there must be an exit close.
The opportunity wanes, nobody wants to give itself the nakedness to break off
and thus we courageously fight in this 
infinite war alone.

Strangely, as this happened shortly after and can not be coincidence,
another scare event 
a futurist biker, fully equipped with helmet, tech gear
flashed by me. surreal
Full speed, a lateral force ?? 


I see a house, a manor house, beyond the trees.
On first thought, wealthy people must live there in this grande mansion
but here in the middle of nowhere?
Suddenly it was gone, and I see only,
time is creeping on from behind.





There is a high peak of this mountain ridge
where the warm sun reaching our skin, but cooling down in the shadows of deep forest.
Cave entrance
We found the remains of 
The virgin forest was a singularity of geometrical perfection
Asymetrical and symetrical shapes
a world, unbenownst to posthuman man
where everything connected together. 
no distinction between fauna and flora.


inumerable tall structures with of ineffable 
with a perimeter of 20 feet
fallen giants, horizontally or 
better in angles, 
a mathematic unknown to civilisation.
seen as 'dead', actually full of life,
hotbed, tangled  

rivers with distinct features
fossils

This forest seemed to be untouched for 300million years.
unbelievable any advanced civilisation, lived there, 
beyond any scientific evidence. 

The smell of green slime, no sound, just simulating energy.

Mathematics
subtract carving 
add moulding?

surds and infinite series are the very root forms of advanced mathematical thought.

black magic (BM), cloaked in teh gray vernacular of psi particles and psi radiation
and transmission and reception. is this transduction?
can it help to grasp the concept of tech?
technical objects exist transductively (change over time, transform over time?)
tech took over, entangled. now on the summit, and looking in the fog.
now downwards. 

</p>




<p>
Caspar David Friedrich, the great hierophant, 
a new subjectivity, my system of organization of visibleness.
a retor l'ordre, 
assembled modules, a collage, a mess created by alien forces.
magical realism
vulnerable
me contemplation of nature
symbols of death.
not trad mimeticism, distorted dark realism
snapshot static, coz 
can't grasp the dynamic beyond 
</p>


<p>
My grandfather was born at at the foot of the majestic Kubany and knew about the 
rites of the Old Ones, even practicing them.  
There were two young in the litter of the wolf, 
and Shewolf became the leader of the  pack.  
One can say this were the ancestors of the we'rewolf pack.  
However, this was  a sign under the the two massive twin peaks belonging to stomping ground.  
Many opted for careers in Eisenbahn and Bleistift in Amerika, 
humans who wear the redskin of The Apache, 
to mimic its reliant design combat
the best of nature hidden in the matrix in the military-industrial complex. 

A land Bloodlands, women and daughters
sprayed with water, frozen bodies shattered into small 
particles 
blood and soil, 
men and sons, workforce
full of envy, scorn, abilities the degenerated brutish apes are not capable of. 
soap and lampshades, 
murder keeping paradise clean, 
but lazy to tidy up after their 
drunken fueled orgies, westerners behaviour into all corners of the world, exemplaryli, perfectly tidy in every aspect, strict to rule and as they are the ideal /idols, 
the others have to do it. 


Over time it dawned on me that the bizarre stories of my grandfather, 
were actually nonsense and a large share of the Great Wisdom.
The puzzling fragments were actually hints to further hollows
in the cryptic thicket of the Bohemian Forest.
Then I had to fill them with speculations, which in turn 
had to be assembled with existing structure. 
Manifestations in a magnificent horrific whole, I was bound to.

It was foretold that if there will 
be no distinction between man and woman, 
will be the end of the world. 
What might sound as fascist fear to a liberal hipster
a grey mass out of once colourful people. 
but colourful matrix outside. 
siemandl


If a church is built the wrong way round, 
'der aufgang aleer auf aufgänge regiert das all' 
a metaphor, for god is dead, headed in the wrong direction,
resurection The cross, arms wide main entrance, west or south (why south) 
st peter, praying to west. 
(pope , praying looking at the people) from 18th century, better built in the market 
the grave 




<p>
Hanson, Moorhead, Bryant, 
I infected them and countless more, 
simply by transgressing their orbits.  
I turned viral to purify their putrid flesh. 
which they unconditionally embraced, 
The dead minds, dissolving in one another, 
 became one in the dark-knight-body.
Trapped there only to breathe, sensory deprivation, 
down to chemical composition and biological bioreceptivity,
a human caterpillar
Laid to waste, abandoned, parasites
But if you ask, 
Am I under their skin
or am I wearing their coat?
Neither, 

permeating the membrane, selective barrier. 
I'm erratic sound. 
I am the dark-bringer, the bottom-dweller. 

I'm always wearing a double coat. 
I took this shape, takes it in material form. 
short hair, extrem temp
guard hair, repel moisture and dirt

annihilation. 
helmet, not only focus but immersed. 
no need for attention.
directly onto the eye
disturb not possible, 



The dust yearns for the wet. 
but why did i manifest, to provoke violence?
intelligence? maybe I am time?
the world does not like what it doesn't know.

My coat, full of grime and stains, displays something truthful
the ticks vomit 
that primes the flesh for further morphing. 

"Culture is dead", said the orange graphity on the wall of the ramshackle mansion, 
nearby the warm moldau, which is now a pig farm.

The wild boars thrive, 
emit debilitating rays if they had been impregnatied 
with some kind of radioactive material.


The wind, leaves are falling in masses, natural agent o.
Then I see the cyclist again, he aged dramatically. Struggling to 
on his way down, sliding, even stopping to not fall on his
spiralling journey downwards.
Was here the Lord of the Mountains involved?


planetschlag war des wie teflon?  Krummau Schreibmaterial (die in china nicht)


The freakish alien apes
had a variety of extremities, like tentacles they were
growing out of their meaty bodies. 
4 of them equipped with further 5 smaller tentacles,
and one of them a thicker one, which was distinctively sticking out
on one side of their body
for grasping objects. What was the objective of doing so?
as they were slowly roaming the land, 
on only their rear paws, unable to walk,
which granted them  majestic buttocks,
a padding.
They enhanced their bodies with technology, 
the decadent generations mostly for ornamental purpose.

Must been to do with their Degenerated teeth, 
hard material, like stone, later then metal, which made believe to be 
immortal and incorruptible.
The graves, Vampire 
Anna Tant, whiteling

I've witnessed how a weakly looking man, who went by the name John, 
and who murdered my brother. 
He strived the woods most lone not with his kin,
and not killing with his fangs but with some artificial thunderbolt
that was followed by a sound of horror. 
echo that burnt deeply in the soul of the forest, 
The abhorrent smell of this creatures, 
triggered the reflex of flight in us,
seeking escape for those able to.
possess supernatural powers 
I previously said murdered, because his motifs
must be that of a maniac.
The true horror was not eating the flesh, drinking the blood but
sometimes habbit of skinning as a trophy
leaving the body to scavengers.
The scalp was in his possession, to touch it or to handle it 
only the exact way he wants it. 

high nobility, 
adolph schwarzenberg, 
lex schwarzenberg.äletere linie, frauenberg.
vampirprinzessin aus krumau, nord-süd richtung skellet
stein in mundhöhle. kopf zwischen beinen. 
3 skelette. 3männer.halswirbel fehlen, rituelle
enthauptung. 


attac and protec

The old ones were capable to breed livestock, 
shoggoats, keeping them in their dens
and used them to work, pasture. 

What survival of his pack?
on our stomping ground, 
Then later period, obvious 
seen in their decadent art 
sculptures made of sand, 
turned into the hostile desert, which can be explored now
difficult. 


They spoke a strange language, influenced by their leader (or ruler) Prince Švarcenberkové
of higher nobility
who shared a huge affinity to the House of Tudor
and wanted to create a prosperous disneyland, near Budweis.
For that chose the most gifted artisans from neighbouring counties, 



<p>
I love exploring the Outside without the aid of high tech and leave the mobile phone at home.bla
one which hasn't internet at all and the other under constant development.
Anyway questing it's better focusing on the movements environment, and relearn to trusting the senses, 
which I often felt deceived upon.


The enourmous silence, only to be interrupted by the great spotted woodpecker 
I feel safe in the former local Forest Sauvage  
and enjoy actually getting lost, knowing find the way back eventually in time.

A deliberate, conscious, constant de /reterritorialization
space becomes territory when it's incorporated in the mind, as they say

That's how I conquer foreign territory, the state border 
the quest, which led me to France in the summer of 2023.

it is good to discover big cities like parithes, in the manner of a flaneuse, 
to find extraordinary people and places, which aren't mapped and def not recommended in any tourist guide.

In Normandy, I got pretty lost once and sore feet, 
wandering endlessly in circles, while following misleading signs which didn't anything signify,
when walking from my base camp in st.aubin, where I've pitched my pavillion,  
to find the Radar facility in Douvres.
Signals to indicate that I was not welcome, me in the gestalt of Miss Bryant, fair hair 
mistaken me for a German spy, handed me the German brochure, which was useless
fell again to the promise of a young and handsome Canadian tour guide. 


But indeed I was sniffing the Radar station, no interest in their nazi memorabilia
the mirror deflection, from the sky




Anyway further interest in magnetism and gravity, knowledge which I will need for later projects.
puzzled by the waves inside of earth, which remains a conundrum, as outer space.


I got a (military) prismatic compass for a reasonable price, to practice navigation
and got a hiking map of 1:25000, as recommended in the video,
of 

that military compass, not for civilian use?
can be used as theodolite


What is magnetic declination? 


dEVIATION in degrees from direction shown on the map 
geographical north pole 
magnetic north pole

As above so below.european
Lodestone "course stone"
magnetite, is attracted my magnets but 
still puzzle, how lodestones become magnets themselves
by lighnting bolts.


durch den günstigen Verlauf der magnetischen Feldlinien in Bayern 
muss diese Abweichung zwishcen magnetischen un geographischer nordrichtung
bei praktischer Anwendung von topografischen Karten nicht berücksichtigt werden


</p>

<p>
intelligence explosion, at a speed of milisecond, singularity,
where each brain dances and floats like a compass needle, 
individual taxonomy of the brain
not just aligned to North, 
where speed and intelligence go to infinity
and destroys The Future of Life Institute. 
gas discharge speed eplosion (8km /s) (33)
faster than the speed of sound
death not perceivable by human flesh. 

Betonung (solid) and gaps in language, 
a tired silence, coz ()hole
brain flickers, on /off simultaneously




The future passed unnoticed, 
integrated in the loup.
Eternal recurrance. 
is now past. 

leave destruction behind, 

how to get consciousness, thru communion. intellect.
cells just survive, 
survival is meaningful, not anymore. 

no communion themselves.
no memory there. 
I can not remember, but is in the flesh (DNA)
Bryant also just can speculate, provoked it.
fissions by accident, without reason,
but when did this happen?
Was there an idle God?

\end{document}
